### 2018-08-31 abstract.tex
Ansh edits incorporated #21

Today climate change pushes humankind in search of new ways to generate 
carbon-free, reliable base load power. Thus,
interest in advanced nuclear energy and particularly \glspl{MSR} has resurged, 
with multiple new companies pursuing commercialization of \gls{MSR} 
designs (e.g. Transatomic, Terrapower, Terrestrial, Moltex Energy, Thorcon). To further 
develop these \gls{MSR} concepts, researchers need simulation tools for analyzing liquid 
fueled molten salt reactor depletion and fuel processing. However, most 
contemporary nuclear reactor physics software is unable to perform high-fidelity 
full-core depletion calculations for a reactor design with online reprocessing. This paper 
introduces a Python package, SaltProc, which couples with the Monte Carlo code, 
SERPENT2, to simulate \gls{MSR} online reprocessing by modeling the changing 
isotopic composition of \gls{MSR} fuel salt. SaltProc capabilities were 
demonstrated for full-core high-fidelity model of the commercial \gls{MSBR} 
concept and compared well to previous results from lower-fidelity analyses.

>>>>

Today,  climate change is driving the search for new ways to generate 
carbon-free, reliable base-load power. Thus,
interest in advanced nuclear energy and particularly \glspl{MSR} has resurged, 
with multiple new companies pursuing commercialization of \gls{MSR} 
designs (e.g. Transatomic, Terrapower, Terrestrial, Moltex Energy, Thorcon). To further 
develop these \gls{MSR} concepts, researchers need simulation tools for analyzing liquid 
fueled \gls{MSR} depletion and fuel processing. However, most 
contemporary nuclear reactor physics software is unable to perform high-fidelity 
full-core depletion calculations for a reactor design with online reprocessing. This paper 
introduces a Python package, SaltProc, which couples with the Monte Carlo code, 
SERPENT2, to simulate \gls{MSR} online reprocessing by modeling the changing 
isotopic composition of \gls{MSR} fuel salt. SaltProc capabilities were 
demonstrated for full-core high-fidelity model of the commercial \gls{MSBR} 
concept and compared well to previous results from lower-fidelity analyses.

### 2018-08-31 introduction.tex
Ansh edits incorporated #21

\section{Introduction}
% State the objectives of the work and provide an adequate background, avoiding
% a detailed literature survey or a summary of the results.
The \gls{MSR} is an advanced nuclear reactor which was developed at \gls{ORNL} 
in the 1950s and was operated in the 1960s. More recently, the \gls{GIF}  
included \glspl{MSR} among the six advanced reactor concepts promising for 
further research and development. 
\glspl{MSR} offer significant improvements ``in the four broad areas of 
sustainability, economics, safety and reliability, and proliferation resistance 
and physical protection" \cite{doe_technology_2002}. To achieve the goals 
formulated by the GIF, \glspl{MSR} attempt to simplify the reactor core and 
improve inherent safety by using liquid fuel.

In the thermal spectrum \gls{MSR}, fluorides of fissile and/or fertile 
materials (i.e. UF$_4$, ThF$_4$,  PuF$_3$, TRU\footnote{ Transuranic 
elements}F$_3$) combine with carrier salts to form a liquid fuel that 
circulates in a loop-type primary circuit \cite{haubenreich_experience_1970}. 
Immediate advantages over traditional, solid-fueled, reactors include 
near-atmospheric pressure in the primary loop, 
relatively high coolant temperature, outstanding neutron economy, improved 
safety parameters, reduced fuel preprocessing, and the ability to continuously 
remove fission products and add fissile and/or fertile elements 
\cite{leblanc_molten_2010}. The thorium-fueled \gls{MSBR} was developed in the 
early 1970s by \gls{ORNL} specifically to explore the promise of the thorium 
fuel cycle, which uses natural thorium instead of enriched uranium. With 
continuous fuel reprocessing, the \gls{MSBR} realizes the advantages of the 
thorium fuel cycle because the $^{233}$U bred from 
$^{232}$Th is almost instantly \footnote{\space $^{232}$Th transmutes into 
$^{233}$Th after capturing a neutron. Next, this isotope decays to $^{233}$Pa 
($\tau_{1/2}$=21.83m), which finally decays to $^{233}$U 
($\tau_{1/2}$=26.967d).} recycled back to the core 
\cite{betzler_modeling_2016}. The chosen fuel salt, LiF-BeF$_2$-ThF$_4$-UF$_4$, has a 
melting point of $499^\circ$C, a low vapor pressure at operating temperatures, 
and good flow and heat transfer properties \cite{robertson_conceptual_1971}. In 
the matter of nuclear fuel cycle, the thorium cycle produces a reduced quantity 
of plutonium and \glspl{MA} compared to the traditional uranium fuel cycle. 
Finally, the \gls{MSR} also could be employed as a converter reactor for 
transmutation of spent fuel from current \glspl{LWR}.

Liquid-fueled systems present a challenge to existing neutron transport and
depletion tools which are typically designed to simulate solid-fueled reactors. 
To handle the material flows and potential online removal and feed of 
liquid-fueled systems, early \gls{MSR} simulation methods at \gls{ORNL} 
integrated neutronics and fuel cycle codes (i.e., \gls{ROD} 
\cite{bauman_rod:_1971}) into operational plant tools (i.e., \gls{MRPP}
\cite{kee_mrpp:_1976}) for \gls{MSR} and reprocessing system design.  Based on 
this approach, recent tools from universities and research institutions can
approximate online refueling \cite{serp_molten_2014}.  Recent research efforts 
in Europe and Asia mainly focus on fast spectrum reactor fuel cycle analysis.
These  couple external tools to neutron transport while depletion codes take into
account continuous feeds and removals in \glspl{MSR}. A summary of recent
efforts are listed in table~\ref{tab:fs_codes}.

@@

Most of these methods are also applicable to thermal spectrum \glspl{MSR}. 
Additional tools developed specifically for thermal \gls{MSR} applications are 
also listed in table~\ref{tab:fs_codes}.

@@

Nuttin \emph{et al.} broke up reactor core geometry into three \gls{MCNP} cells: 
one for salt channels, one for the salt plena above and below the core and the 
last cell for the annulus, consequently, the two-region reactor core was 
approximated by one region with averaged fuel/moderator ratio 
\cite{nuttin_potential_2005}.  A similar approach was used by Powers \emph{et 
al.}, Betzler \emph{et al.}, and Jeong \emph{et al.} 
\cite{powers_new_2013,powers_inventory_2014,betzler_modeling_2016, 
betzler_molten_2017, jeong_development_2014, jeong_equilibrium_2016}. This approach 
misrepresents the two-region breeder reactor concept. The unit-cell or one-region 
models may produce reliable results for homogeneous reactor cores (i.e. 
\gls{MSFR}, \gls{MOSART}) or for one-region single-fluid reactor designs (i.e. 
\gls{MSRE}). However, a two-region \gls{MSBR} must be simulated using a whole-core 
model to capture different neutron transport characteristics in the inner and 
outer regions of the core. In particular, most fissions happens in the inner 
region while breeding occurs in the outer zone.

@@

The complex \gls{MSBR} geometry is challenging to describe in software input, 
and, 
usually, researchers make significant geometric simplifications to model it 
\cite{park_whole_2015}. This study leverages extensive computational 
resources to avoid these geometric approximations in order to accurately capture 
breeding behavior.

>>>>

\section{Introduction}
% State the objectives of the work and provide an adequate background, avoiding
% a detailed literature survey or a summary of the results.
The \gls{MSR} is an advanced nuclear reactor which was developed at \gls{ORNL} 
in the 1950s and was operated in the 1960s. More recently, the \gls{GIF}  
included \glspl{MSR} among the six most promising advanced reactor concepts for 
further research and development. 
\glspl{MSR} offer significant improvements ``in the four broad areas of 
sustainability, economics, safety and reliability, and proliferation resistance 
and physical protection" \cite{doe_technology_2002}. To achieve the goals 
formulated by the GIF, \glspl{MSR} attempt to simplify the reactor core and 
improve inherent safety by using liquid fuel.

In the thermal spectrum \gls{MSR}, fluorides of fissile and/or fertile 
materials (i.e. UF$_4$, ThF$_4$,  PuF$_3$, TRU\footnote{ Transuranic 
elements}F$_3$) combine with carrier salts to form a liquid fuel that 
circulates in a loop-type primary circuit \cite{haubenreich_experience_1970}. 
Immediate advantages over traditional, solid-fueled, reactors include 
near-atmospheric pressure in the primary loop, 
relatively high coolant temperature, outstanding neutron economy, improved 
safety parameters, reduced fuel preprocessing, and the ability to continuously 
remove fission products and add fissile and/or fertile elements 
\cite{leblanc_molten_2010}. The thorium-fueled \gls{MSBR} was developed in the 
early 1970s by \gls{ORNL} to explore specifically the promise of the thorium 
fuel cycle, which uses natural thorium instead of enriched uranium. With 
continuous fuel reprocessing, the \gls{MSBR} realizes the advantages of the 
thorium fuel cycle because the $^{233}$U bred from 
$^{232}$Th is almost instantly\footnote{\space $^{232}$Th transmutes into 
$^{233}$Th after capturing a neutron. Next, this isotope decays to $^{233}$Pa 
($\tau_{1/2}$=21.83m), which finally decays to $^{233}$U 
($\tau_{1/2}$=26.967d).} recycled back into the core 
\cite{betzler_modeling_2016}. The chosen fuel salt, LiF-BeF$_2$-ThF$_4$-UF$_4$, has a 
melting point of $499^\circ$C, a low vapor pressure at operating temperatures, 
and good flow and heat transfer properties \cite{robertson_conceptual_1971}. In 
the matter of nuclear fuel cycle, the thorium cycle produces a reduced quantity 
of plutonium and \glspl{MA} compared to the traditional uranium fuel cycle. 
Finally, the \gls{MSR} also could be employed as a converter reactor for 
transmutation of spent fuel from current \glspl{LWR}.

Liquid-fueled systems present a challenge to existing neutron transport and
depletion tools, which are typically designed to simulate solid-fueled reactors. 
To handle the material flows and potential online removal and feed of 
liquid-fueled systems, early \gls{MSR} simulation methods at \gls{ORNL} 
integrated neutronics and fuel cycle codes (i.e., \gls{ROD} 
\cite{bauman_rod:_1971}) into operational plant tools (i.e., \gls{MRPP}
\cite{kee_mrpp:_1976}) for \gls{MSR} and reprocessing system design.  Based on 
this approach, recent tools from universities and research institutions can
approximate online refueling \cite{serp_molten_2014}. A summary of recent
efforts is listed in table~\ref{tab:fs_codes}.

@@

@@

Nuttin \emph{et al.} broke up reactor core geometry into three \gls{MCNP} cells: 
one for salt channels, one for the salt plena above and below the core and the 
last cell for the annulus. Consequently, the two-region reactor core was 
approximated by one region with averaged fuel/moderator ratio 
\cite{nuttin_potential_2005}.  A similar approach was used by Powers \emph{et 
al.}, Betzler \emph{et al.}, and Jeong \emph{et al.} 
\cite{powers_new_2013,powers_inventory_2014,betzler_modeling_2016, 
betzler_molten_2017, jeong_development_2014, jeong_equilibrium_2016}. This approach 
misrepresents the two-region breeder reactor concept. The unit-cell or one-region 
models may produce reliable results for homogeneous reactor cores (i.e. 
\gls{MSFR}, \gls{MOSART}) or for one-region single-fluid reactor designs (i.e. 
\gls{MSRE}). However, a two-region \gls{MSBR} must be simulated using a whole-core 
model to capture different neutron transport characteristics in the inner and 
outer regions of the core. In particular, most fissions happens in the inner 
region while breeding occurs in the outer zone.

@@

The complex \gls{MSBR} geometry is challenging to describe in software input, 
and usually researchers make significant geometric simplifications to model it 
\cite{park_whole_2015}. This study leverages extensive computational 
resources to avoid these geometric approximations in order to accurately capture 
breeding behavior.

### 2018-08-31 methods.tex
Ansh edits incorporated #21

The ability of liquid-fueled systems to continuously remove fission products and add 
fissile and/or fertile elements is the main challenge for depletion simulations. 
The python package introduced in this work, SaltProc, takes into account online 
separations and feeds using the SERPENT 2 continuous-energy Monte Carlo neutron 
transport and depletion code.

@@

Since reactor graphite experiences significant dimensional changes due to 
neutron irradiation, the reactor core was designed for periodic replacement. 
Based on the experimental irradiation data from \gls{MSRE}, the core graphite 
lifetime is about 4 years and reflector graphite lifetime is 30 years 
\cite{robertson_conceptual_1971}.

There are eight symmetric graphite slabs with a width of 15.24 cm in zone II, 
one of which is illustrated in Figure~\ref{fig:serpent_zoneII}. The holes in 
the centers are for the core lifting rods used during the core replacement 
operations. These holes also allow a portion of the fuel salt to flow to the 
top of the vessel for cooling the top head and axial reflector. 
Figure~\ref{fig:serpent_zoneII} also shows
the 5.08-cm-wide annular 
space between the removable core graphite in zone II-B and the permanently 
mounted reflector graphite. This annulus consists entirely of fuel salt, 
provides space for moving the core assembly, helps compensate for the elliptical 
dimensions of the reactor vessel, and serves to reduce the damaging flux at the 
surface of the graphite reflector blocks. In this work, all figures of the core 
were generated using the built-in SERPENT 2 plotter.

@@

\subsubsection{Core zone II}
Zone II which is undermoderated, surrounds zone I. Combined with the bounding 
radial reflector, zone II serves to diminish neutron leakage. Two kinds of 
elements form this zone: large-diameter fuel channels (zone II-A) and 
radial graphite slats (zone II-B).

@@

The sophisticated, irregular shapes of the fuel elements challenge an accurate 
representation of zone II-B.  
The suggested design \cite{robertson_conceptual_1971} of zone II-B has 8 
irregularly-shaped graphite elements as well as dozens of salt channels. 
These graphite elements were simplified into right-circular cylindrical shapes  
with central channels. Figure~\ref{fig:serpent_zoneII} illustrates this core 
region in the SERPENT model. The volume of fuel salt in zone II was kept 
exactly 37\%, so that this simplification did not considerably change the core 
neutronics. Simplyfying the eight edge channels was te only simplification made 
to the \gls{MSBR} geometry in this work.

@@

\subsubsection{Material composition and normalization parameters}
The fuel salt, reactor graphite, and modified Hastelloy-N\footnote{ 
Hastelloy-N is very common in reactors now but have been studied and developed 
at \gls{ORNL} in a program that started in 1950s.} 
are all materials created at \gls{ORNL} specifically for the \gls{MSBR}.
The initial fuel salt used the same 
density (3.35 g/cm$^3$) and composition LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$ 
(71.75-16-12-0.25 mole \%) as the \gls{MSBR} design 
\cite{robertson_conceptual_1971}. The lithium in the molten salt fuel is fully 
enriched in $^{7}$Li because $^{6}$Li is a very strong neutron poison and 
becomes tritium upon neutron capture.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[h!]
        %\centering
        \caption{Summary of principal data for MSBR 
        \cite{robertson_conceptual_1971}.}
        \begin{tabularx}{\textwidth}{ s  s}
        \hline
                Thermal capacity of reactor           		& 2250 MW(t)
                \\ Net electrical output                 		& 1000 
        MW(e) \\  Net thermal efficiency        				
        & 44.4\%
                \\  Salt volume fraction in central zone I		& 0.13
                \\ Salt volume fraction in outer zone II       & 0.37
                \\ Fuel salt inventory (Zone I)                & 8.2 m$^3$	
        \\ Fuel salt inventory (Zone II)               & 10.8 m$^3$	\\ Fuel 
        salt inventory (annulus)               & 3.8 m$^3$	\\  Total fuel 
        salt inventory                   & 48.7 m$^3$	\\ Fissile mass in fuel 
        salt                   & 1303.7 kg	\\ Fuel salt components                  
                               & LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$	\\  
        Fuel salt composition                 & 71.75-16-12-0.25 mole\%
                \\
                Fuel salt density                    & 3.35 g/cm$^3$
                \\ \hline
        \end{tabularx}
        \label{tab:msbr_tab}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Online reprocessing method}
Removing specific chemical elements from a molten salt 
requires intelligent design (e.g., chemical separations equipment design, 
fuel salt flows to equipment) and has a considerable economic cost. All 
liquid-fueled \gls{MSR} designs involve varying levels of online fuel 
processing. Minimally, volatile gaseous fission products (e.g. Kr, Xe) escape 
from the fuel salt during routine reactor operation and must be captured. 
Additional systems might be used to enhance removal of those elements. Most 
designs also call for the removal of noble and rare earth metals from the core 
since these metals act as neutron poisons. Some designs suggest a more complex 
list of elements to process (figure ~\ref{fig:periodic_tab}), including the 
temporary removal of protactinium or other regulation of the 
actinide inventory \cite{ahmad_neutronics_2015}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[ht!]
        \centering
        \caption{The effective cycle times for protactinium and fission 
        products removal (reproduced from \cite{robertson_conceptual_1971}).}
        \begin{tabularx}{\textwidth}{ x | s | x }
        \hline Processing group & \qquad\qquad\qquad Nuclides & Cycle time (at 
                full power) \\ \hline Rare earths & Y, La, Ce, Pr, Nd, Pm, Sm, 
                Gd & 50 days \\ \qquad & Eu & 500 days \\ Noble metals & Se, 
                Nb, Mo, Tc, Ru, Rh, Pd, Ag, Sb, Te & 20 sec \\
        Seminoble metals & Zr, Cd, In, Sn & 200 days \\
        Gases & Kr, Xe & 20 sec \\ Volatile fluorides & Br, I & 60 days \\
        Discard & Rb, Sr, Cs, Ba & 3435 days \\ Salt discard & Th, Li, Be, F & 
                3435 days \\ Protactinium & $^{233}$Pa & 3 days \\ Higher 
                nuclides & $^{237}$Np, $^{242}$Pu & 16 years \\  \hline
        \end{tabularx}
        \label{tab:reprocessing_list}
\end{table}
Th removal rates vary among nuclides in this reactor concept which dictate the 
necessary resolution of depletion calculations. If the depletion time intervals 
are very short, an enormous number of depletion steps are required to obtain 
the equilibrium composition. On the other hand, if the depletion  calculation 
time interval is too long, the impact of short-lived fission products is not 
captured. To compromise, the time interval for depletion calculations in this 
model was selected as 3 days to correlate with the removal interval of 
$^{233}$Pa and $^{232}$Th was continuously added to maintain the initial mass 
fraction of $^{232}$Th.

@@

The tool structure and capabilities of SaltProc are similar to the ChemTriton tool 
developed in \gls{ORNL} for SCALE \cite{powers_new_2013}. SaltProc is coupled 
with the Monte Carlo SERPENT 2
software to simulate online reprocessing for irregular full-core 
geometry with high fidelity.  The primary function of SaltProc is to 
manage material streams while
SERPENT 2 performs the computationally heavy work, namely neutron 
transport and depletion
calculations. Saltproc is defined as a python class, where each material stream 
is defined as a isotopic atomic density
vector variable. This allows tracking of time-sensitive material streams such 
as the
$^{233}$Pa tank in the \gls{MSBR}. The user can define the reprocessing 
parameters, such as the reprocessing interval and removal efficiency.  In 
addition, SaltProc provides a set of functions for each stream: read and write 
isotopic data in/from database, separate out specific elements from stream with 
defined efficiency, feed in specific isotopes to stream, and maintain constant 
number density of specific nuclide in the core. These attributes and functions 
are crucial to simulating the operation of a complex, multi-zone, multi-fluid 
\gls{MSR} and are sufficiently general to represent myriad reactor systems.

SaltProc, currently in active development in Github (https://github.com/ 
arfc/saltproc), leverages unit tests and continuous integration for 
sustainable development. There is also documentation
generated through Sphinx document generator for ease of use. In future 
releases, we plan to 
implement
support for entirely user-customized reprocessing strategies, two-region \gls{MSR} modeling 
capabilities, and decay modeling in tanks.

@@

\begin{figure}[ht!] % replace 't' with 'b' to \centering
  \includegraphics[width=0.75\textwidth]{saltproc_flowchart.pdf}
  \caption{Flow chart for the Saltproc python package.}
  \label{fig:saltproc_flow}
\end{figure}
SaltProc can manage as many material streams as desired. It also may work with 
multiple depletion materials. At the end of a each depletion step, SaltProc 
reads the depleted compositions and tracks each material stream individually. 
Following this, it applies chemical separation functions to fuel stream 
vectors. These vectors then form a matrix (isotopics x timesteps) which 
SaltProc stores in an HDF5 database and prints into the SERPENT 2 composition 
file for the next depletion calculation.

Saltproc datasets are timseries, meaning that every value is recorded every 
timestep. The datasets SaltProc produces are listed below,
where the values inside the parenthesis are the dataset sizes:

>>>>

The ability of liquid-fueled systems to continuously remove fission products and add 
fissile and/or fertile elements is the main challenge for depletion simulations. 
The python package introduced in this work, SaltProc, takes into account online 
separations and feeds using the SERPENT 2 continuous-energy Monte Carlo neutron 
transport and depletion code. In this work, all figures of the core model
were generated using the built-in SERPENT 2 plotter.

@@

Since reactor graphite experiences significant dimensional changes due to 
neutron irradiation, the reactor core was designed for periodic replacement. 
Based on the experimental irradiation data from the \gls{MSRE}, the core graphite 
lifetime is about 4 years and the reflector graphite lifetime is 30 years 
\cite{robertson_conceptual_1971}.

There are eight symmetric graphite slabs with a width of 15.24 cm in zone II, 
one of which is illustrated in Figure~\ref{fig:serpent_zoneII}. The holes in 
the centers are for the core lifting rods used during the core replacement 
operations. These holes also allow a portion of the fuel salt to flow to the 
top of the vessel for cooling the top head and axial reflector. 
Figure~\ref{fig:serpent_zoneII} also shows
the 5.08-cm-wide annular 
space between the removable core graphite in zone II-B and the permanently 
mounted reflector graphite. This annulus consists entirely of fuel salt, 
provides space for moving the core assembly, helps compensate for the elliptical 
dimensions of the reactor vessel, and serves to reduce the damaging flux at the 
surface of the graphite reflector blocks.

@@

\subsubsection{Core zone II}
Zone II, which is undermoderated, surrounds zone I. Combined with the bounding 
radial reflector, zone II serves to diminish neutron leakage. Two kinds of 
elements form this zone: large-diameter fuel channels (zone II-A) and 
radial graphite slats (zone II-B).

@@

The sophisticated, irregular shapes of the fuel elements challenge an accurate 
representation of zone II-B.  
The suggested design \cite{robertson_conceptual_1971} of zone II-B has 8 
irregularly-shaped graphite elements as well as dozens of salt channels. 
These graphite elements were simplified into right-circular cylindrical shapes  
with central channels. Figure~\ref{fig:serpent_zoneII} illustrates this core 
region in the SERPENT model. The volume of fuel salt in zone II was kept 
exactly 37\%, so that this simplification did not considerably change the core 
neutronics. Simplyfying the eight edge channels was the only simplification made 
to the \gls{MSBR} geometry in this work.

@@

\subsubsection{Material composition and normalization parameters}
The fuel salt, reactor graphite, and modified Hastelloy-N\footnote{ 
Hastelloy-N is very common in reactors now but has been studied and developed 
at \gls{ORNL} in a program that started in 1950s.} 
are all materials created at \gls{ORNL} specifically for the \gls{MSBR}.
The initial fuel salt used the same 
density (3.35 g/cm$^3$) and composition LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$ 
(71.75-16-12-0.25 mole \%) as the \gls{MSBR} design 
\cite{robertson_conceptual_1971}. The lithium in the molten salt fuel is fully 
enriched to 100\% $^{7}$Li because $^{6}$Li is a very strong neutron poison and 
becomes tritium upon neutron capture.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[h!]
        %\centering
        \caption{•} of principal data for MSBR 
        \cite{robertson_conceptual_1971}.}
        \begin{tabularx}{\textwidth}{ s  s}
        \hline
                Thermal capacity of reactor           		& 2250 MW(t)
                \\ Net electrical output                 		& 1000 
        MW(e) \\  Net thermal efficiency        				
        & 44.4\%
                \\  Salt volume fraction in central zone I		& 0.13
                \\ Salt volume fraction in outer zone II       & 0.37
                \\ Fuel salt inventory (Zone I)                & 8.2 m$^3$	
        \\ Fuel salt inventory (Zone II)               & 10.8 m$^3$	\\ Fuel 
        salt inventory (annulus)               & 3.8 m$^3$	\\  Total fuel 
        salt inventory                   & 48.7 m$^3$	\\ Fissile mass in fuel 
        salt                   & 1303.7 kg	\\ Fuel salt components                  
                               & LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$	\\  
        Fuel salt composition                 & 71.75-16-12-0.25 mole\%
                \\
                Fuel salt density                    & 3.35 g/cm$^3$
                \\ \hline
        \end{tabularx}
        \label{tab:msbr_tab}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Online reprocessing method}
Removing specific chemical elements from a molten salt 
requires intelligent design (e.g., chemical separations equipment design, 
fuel salt flows to equipment) and has a considerable economic cost. All 
liquid-fueled \gls{MSR} designs involve varying levels of online fuel 
processing. Minimally, volatile gaseous fission products (e.g. Kr, Xe) escape 
from the fuel salt during routine reactor operation and must be captured. 
Additional systems might be used to enhance removal of those elements. Most 
designs also call for the removal of noble and rare earth metals from the core 
since these metals act as neutron poisons. Some designs suggest a more complex 
list of elements to process (figure~\ref{fig:periodic_tab}), including the 
temporary removal of protactinium or other regulation of the 
actinide inventory \cite{ahmad_neutronics_2015}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[ht!]
        \centering
        \caption{The effective cycle times for protactinium and fission 
        products removal (reproduced from \cite{robertson_conceptual_1971}).}
        \begin{tabularx}{\textwidth}{ x | s | x }
        \hline Processing group & \qquad\qquad\qquad Nuclides & Cycle time (at 
                full power) \\ \hline Rare earths & Y, La, Ce, Pr, Nd, Pm, Sm, 
                Gd & 50 days \\ \qquad & Eu & 500 days \\ Noble metals & Se, 
                Nb, Mo, Tc, Ru, Rh, Pd, Ag, Sb, Te & 20 sec \\
        Seminoble metals & Zr, Cd, In, Sn & 200 days \\
        Gases & Kr, Xe & 20 sec \\ Volatile fluorides & Br, I & 60 days \\
        Discard & Rb, Sr, Cs, Ba & 3435 days \\ Salt discard & Th, Li, Be, F & 
                3435 days \\ Protactinium & $^{233}$Pa & 3 days \\ Higher 
                nuclides & $^{237}$Np, $^{242}$Pu & 16 years \\  \hline
        \end{tabularx}
        \label{tab:reprocessing_list}
\end{table}
The removal rates vary among nuclides in this reactor concept which dictate the 
necessary resolution of depletion calculations. If the depletion time intervals 
are very short, an enormous number of depletion steps are required to obtain 
the equilibrium composition. On the other hand, if the depletion  calculation 
time interval is too long, the impact of short-lived fission products is not 
captured. To compromise, the time interval for depletion calculations in this 
model was selected as 3 days to correlate with the removal interval of 
$^{233}$Pa and $^{232}$Th was continuously added to maintain the initial mass 
fraction of $^{232}$Th.

@@

The tool structure and capabilities of SaltProc are similar to the ChemTriton tool 
developed in \gls{ORNL} for SCALE \cite{powers_new_2013}. SaltProc is coupled 
with the Monte Carlo SERPENT 2
software to simulate online reprocessing for irregular full-core 
geometry with high fidelity.  The primary function of SaltProc is to 
manage material streams while SERPENT 2 performs the neutron 
transport and depletioncalculations. Saltproc is defined as a python class, where 
each material stream is defined as a isotopic atomic density
vector variable. This allows tracking of time-sensitive material streams such 
as the 	$^{233}$Pa tank in the \gls{MSBR}. The user can define the reprocessing 
parameters, such as the reprocessing interval and removal efficiency.  In 
addition, SaltProc provides a set of functions for each stream: read and write 
isotopic data in/from database, separate out specific elements from stream with 
defined efficiency, feed in specific isotopes to stream, and maintain constant 
number density of specific nuclide in the core. These attributes and functions 
are crucial to simulating the operation of a complex, multi-zone, multi-fluid 
\gls{MSR} and are sufficiently general to represent myriad reactor systems.

SaltProc, currently in active development on Github (https://github.com/ 
arfc/saltproc), leverages unit tests and continuous integration for 
sustainable development. There is also documentation
generated through Sphinx document generator for ease of use. In future 
releases, we plan to 
implement
support for entirely user-customized reprocessing strategies, two-region \gls{MSR} modeling 
capabilities, and decay modeling in tanks.

@@

\begin{figure}[ht!] % replace 't' with 'b' to \centering
  \includegraphics[width=0.75\textwidth]{saltproc_flowchart.pdf}
  \caption{Flow chart for the Saltproc python package.}
  \label{fig:saltproc_flow}
\end{figure}
SaltProc can manage as many material streams as desired. It also may work with 
multiple depletion materials. At the end of each depletion step, SaltProc 
reads the depleted compositions and tracks each material stream individually. 
Following this, it applies chemical separation functions to fuel stream 
vectors. These vectors then form a matrix (isotopics x timesteps) which 
SaltProc stores in an HDF5 database and prints into the SERPENT 2 composition 
file for the next depletion calculation.

Saltproc datasets are time-series, meaning that every value is recorded every 
timestep. The datasets SaltProc produces are listed below,
where the values inside the parenthesis are the dataset sizes:
